---
title: "not so Simple document!!! too fast!!!"
author: "Zai...brain damaged"
output: 
  html_document:
    toc: true #table of content
    toc_float: true
---

I'm an R Markdown document! 

# Section 0: library

```{r echo = FALSE, message = F}
library(tidyverse)
# echo hides code chunk, message = F hide the message/suggestions/flags
# eval = F means let the code do not run
```


# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100) #only codein ``` will run
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: a tibble

```{r}
plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2*x + rnorm(1000)
  )

head(plot_df)
```

# Section 4: plots

```{r echo = FALSE}
ggplot(plot_df, aes(x = x)) + geom_histogram()

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
#echo = F meaning removing the code display in the html
```

# Section 5: learning assessment 2

This plot shows the distribution of the absolutes value of $X \sim N(1, 1)$

```{r learning assessment 2}
la_df = tibble(
  num_var = rnorm(500, mean = 1),
  log_var = num_var > 0, # logical factor means T or F
  abs_var = abs(num_var)
)

ggplot(la_df, aes(x = abs_var)) + geom_histogram()
```

The median is `r round(median(pull(la_df, num_var)), 2)`.



Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# Section 7: learning Assessment 3

* The mean is `r round(mean(pull(la_df, num_var)),2)`
* The median is `r round(median(pull(la_df, num_var)),2)`
* The SD is `r round(sd(pull(la_df, num_var)),2)`
